\chapter{Conclusion}

Thermal hyperspectral data delivers unique information about temperature and emissivity of the Earth surface which results in many application in both scientific and commercial fields. However, derivation of these quantities leads to the underdetermined system of equations, as was discussed in the Chapter \ref{chap:TES}. Many approaches have been developed to overcome this problem among which the TES algorithm is the most widely known and used. 

The TES algorithm is well established and popular for several reasons: it retrieves temperature and emissivity of natural surfaces simultaneously without any previous knowledge of surface type and it is widely applicable to range of multispectral and hyperspectral sensors. This suggests that the algorithm is a good benchmark for temperature and emissivity separation. Any improvement to the TES algorithm can benefit processing of thermal data from many sources.

Chapter \ref{chap:TES} introduced a module that estimates temperature and emissivity from an approximation of the relationship between brightness temperature and emissivity. The new module replaces the NEM module in the original TES to create an algorithm we call OSTES. The OSTES algorithm was chosen for processing image data acquired from TASI sensors operated by Global Change Research Institute CAS (Brno, Czech Republic). The pre-processing chain is applied to the image data before passing them to the OSTES algorithm. The individual pre-processing steps were described in the Chapter \ref{chap:Data} and the attachment of the OSTES to the pre-processing chain is discussed in the Chapter \ref{chap:OSTESValid}.

The performance of OSTES was firstly tested on a set of simulated data recomputed with respect to ASTER, AHS and TASI response functions. Results show that temperature estimations using OSTES are more accurate and precise than TES for samples with low spectral contrast. It should be noted that this improvement is of modest size when compared to the already accurate results that can be obtained with TES. OSTES and TES perform similarly for samples with a high spectral contrast. The results also reveal that OSTES is less sensitive to variations in atmospheric conditions.

The OSTES was also compared against the ASTER standard product AST\_09T over the Caspian Sea and Lake Baikal. By comparing the OSTES results to ASTER standard products AST\_08 (temperature) and AST\_05 (emissivity) we found that temperature retrievals of both algorithms are very close. However, it was also found that temperatures included in AST\_08 product are not consistent with emissivities delivered by AST\_05 product in the sense of (\ref{eq:emissivityComputation}). Thus emissivities were recomputed based on downwelling and land-leaving radiance from AST\_09T and temperature from AST\_08. 

Comparing all three emissivity retrievals over the Caspian Sea in different seasons shows that emissivity from AST\_05 to be closest and recomputed emissivity to be the furthest from expected sea water emissivity values extracted from ASTER Spectral Library, except in the June and September scenes, which are expected to have the largest water vapour burden in the atmosphere. It is also observed that the AST\_05 emissivities over Lake Baikal exhibit step discontinuities. In the same region OSTES and recomputed emissivities tend to be smoother with OSTES emissivities being closer to expected value of water emissivity. All emissivity retrievals are probably affected by inaccurate atmospheric corrections since none of the obtained spectra had emissivity values close to expected values.

The performance of the OSTES and TES was tested on image data acquired by TASI sensor and validated against \textit{in-situ} measurements. The emissivity retrievals from both algorithms follow \textit{in-situ} measurements well in most of the cases. However, it is not possible to observe the improvement introduced by the OSTES algorithm, when comparing to the TES results, due to the imperfect atmospheric corrections.

We conclude that improvements in atmospheric compensation will be crucial for further improvements in emissivity results. Thus, further work should be focused on this topic. Additional improvements in OSTES will consider modifications of cost function represented in (\ref{eq:costFunction}) and illustrated in Fig. \ref{fig:FunctionCode}. Better approximations of the relationship between brightness temperature and emissivity could result in better temperature and emissvity retrievals.

%We believe it is important to validate the performance of future improvements by using data acquired by a variety of multispectral and hyperspectral sensors, such as AHS and TASI. Additional improvements in OSTES will consider modifications of cost function represented in (\ref{eq:costFunction}) and illustrated in Fig. \ref{fig:FunctionCode}. Better approximations of the relationship between brightness temperature and emissivity could result in better temperature and emissvity retrievals. 

The OSTES algorithm is preferred mainly because of higher precision and accuracy under conditions of low spectral contrast, and because of the consistency between retrieved temperature and emissivity. We believe that implementing OSTES to processing chain of TASI image data will benefit application for landscape assessment. We also hope that improvements introduced by OSTES will help to enhance the quality of temperature and emissivity results in general.

%New approaches in airborne thermal image processing for landscape assessment

%Since TES plays important role in the TIR data processing, we suggest to use OSTES instead of TES mainly because of higher precision and accuracy under conditions of low spectral contrast, and because of the consistency between retrieved temperature and emissivity. We hope that improvements introduced by OSTES will help to enhance the quality of temperature and emissivity results.