\begin{thebibliography}{10}
\addcontentsline{toc}{chapter}{References}
%\makeatletter
%\def\@biblabel#1{}
%\let\old@bibitem\bibitem
%\def\bibitem#1{\old@bibitem{#1}\leavevmode\kern-\bibindent}
%\makeatother

%\footnotesize

\section*{Own publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MOJE PUBLIKACE
%\bibitem{hf_ibcst} Holešovský, J., Fusek, M. (2015). Metody analýzy extrémních hodnot a~jejich softwarová implementace. Odesláno k~publikaci.
%%
%\bibitem{hfm_hsj} Holešovský, J., Fusek, M., Blachut, V., Michálek, J. (2015). Comparison of precipitation extremes estimation using parametric and nonparametric methods. \emph{Hydrological Sciences Journal}. Přijato k~publikaci. DOI 10.1080/02626667.2015.1111517.
%%
%\bibitem{hfm1} Holešovský, J., Fusek, M., Michálek, J. (2015). Modelling of precipitation extremes using parametric and nonparametric methods with automated threshold selection. \emph{International Journal of Mathematics and Computers in Simulation} \textbf{9}, 94-102.
%%
%\bibitem{hfm_recko} Holešovský, J., Fusek, M., Michálek, J. (2014). Automated threshold selection for parametric and non-parametric estimates of intensity-duration-frequency curves. \emph{Proceedings of the 1st International Conference on Mathematical Methods \& Computational Techniques in Science \& Engineering, MMCTSE 2014}. Athens, Greece. ISBN 987-1-61804-256-9.
%%
%\bibitem{hfm_mendel} Holešovský, J., Fusek, M., Michálek, J. (2014). Extreme value estimation for correlated observations. \emph{20th International Conference on Soft Computing MENDEL 2014.} Brno, Czech Republic, 359-364.
%%
%\bibitem{hp_pdmu} Holešovský, J., Popela, P. (2012). Stochastic Extensions of a~Traffic Assignment Problem. \emph{XX International Conference PDMU-2012: Problems of Decision Making under Uncertainties, Proceeding - Applied Papers.} Brno, Czech Republic, 61-70. ISBN 978-80-7231-897-1.
%%
%\bibitem{hpr_mendel} Holešovský, J., Popela, P., Roupec, J. (2013). Disruption in Congested Networks. \emph{Proceedings of 19th International Conference on Soft Computing MENDEL 2013.} Brno, Czech Republic, 191-196. ISBN 978-80-214-4755-4.
%%
%\bibitem{hz_ryby} Olejníčková, Z., Holešovský, J., Vávrová, M., Králová, Z., Michálek, J. (2014). Methylmercury in tissues of fish from the Svratka River, the Czech Republic. \emph{Fresenius Environmental Bulletin} \textbf{23}(12b), 3319-3324.
%%
%\bibitem{hs_zizaly} Škarková, P., Zlámalová Gargošová, H., Holešovský, J., Vávrová, M., Michálek, J., Olejníčková, Z. (2015). Application of statistical methods for ecotoxicological data evaluation. \emph{Fresenius Environmental Bulletin} \textbf{24}(5), 1692-1698.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{References}

\addcontentsline{toc}{section}{References}

\bibitem{BH09} BALDRIDGE, A.M., S.J. HOOK, C.I. GROVE and G. RIVERA. The ASTER spectral library version 2.0. \textit{Remote Sensing of Environment}. 2009, vol. 113, issue 4, s. 711-715 [cit. 2015-04-24]. DOI: 10.1016/j.rse.2008.11.007.

\bibitem{BP96} BARDUCCI, A. and I. PIPPI. Temperature and emissivity retrieval from remotely sensed images using the "Grey body emissivity" method. \textit{IEEE Transactions on Geoscience and Remote Sensing}. vol. 34, issue 3, s. 681-695. DOI: 10.1109/36.499748. Dostupné z: http://ieeexplore.ieee.org/lpdocs/epic03/wrapper.htm?arnumber=499748

\bibitem{BG06} BERK, A., G.P. ANDERSON, P.K. ACHARYA, L.S. BERNSTEIN, L. MURATOV, J. LEE, M. FOX, S.M. ADLER-GOLDEN, J.H. CHETWYND, JR., M.L. HOKE, R.B. LOCKWOOD, J.A. GARDNER, T.W. COOLEY, C.C. BOREL, P.E. LEWIS and E.P. SHETTLE. MODTRAN5: 2006 update. In: \textit{Algorithms and Technologies for Multispectral, Hyperspectral, and Ultraspectral Imagery XII}. 2006 [cit. 2015-04-24]. DOI: 10.1117/12.665077.

\bibitem{B11} BORBAS, E., S.W. SEEMANN, KERN, MOY, J. LI, L. GUMLEY and W.P. MENZEL. MODIS Atmospheric Profile Retrieval - ATBD. 2011. 

\bibitem{B98} BOREL, C.C. Surface emissivity and temperature retrieval for a hyperspectral sensor. IGARSS '98. Sensing and Managing the Environment. \textit{IEEE International Geoscience and Remote Sensing}. Symposium Proceedings. (Cat. No.98CH36174). IEEE, 1998, 546-549 vol.1. DOI: 10.1109/IGARSS.1998.702966. Available at: http://ieeexplore.ieee.org/lpdocs/epic03/wrapper.htm?arnumber=702966

\bibitem{B07} BOREL, C. Error analysis for a temperature and emissivity retrieval algorithm for hyperspectral imaging data. \textit{International Journal of Remote Sensing} [online]. 2008, vol. 29, 17-18, s. 5029-5045 [cit. 2015-04-24]. DOI: 10.1080/01431160802036540.

\bibitem{G95} GILLESPIE, A. R., 1986. Lithologic mapping of silicate rocks using TIMS. Dostupné z: http://ntrs.nasa.gov/search.jsp?R=19870007685

\bibitem{G99} GILLESPIE, A., S. ROKUGAWA, S. HOOK, T. MATSUNAGA and A.B. KAHLE. \textit{Temperature/Emissivity Separation Algorithm Theoretical Basis Document, Version 2.4}. Pasadena: Jet Propulsion Laboratory, 1999, 64 p.

\bibitem{GR98} GILLESPIE, A., S. ROKUGAWA, T. MATSUNAGA, J.S. COTHERN, S. HOOK and A.B. KAHLE. A temperature and emissivity separation algorithm for Advanced Spaceborne Thermal Emission and Reflection Radiometer (ASTER) images. \textit{IEEE Transactions on Geoscience and Remote Sensing} [online]. 1998, vol. 36, issue 4, s. 1113-1126 [cit. 2015-04-24]. DOI: 10.1109/36.700995.

\bibitem{GG00} GU, D., A.R. GILLESPIE, A.B. KAHLE and F.D. PALLUCONI. Autonomous atmospheric compensation (AAC) of high resolution hyperspectral thermal infrared remote-sensing imagery. \textit{IEEE Transactions on Geoscience and Remote Sensing}. 2000, vol. 38, issue 6, s. 2557-2570 [cit. 2015-04-24]. DOI: 10.1109/36.885203.

\bibitem{HF14} HANUŠ, J., T. FABIÁNEK, V. KAPLAN a L. HOMOLOVÁ. FLYING LABORATORY OF IMAGING SYSTEMS (FLIS) AT CZECHGLOBE. In: SGEM2014 Conference Proceedings. 2014, s. 177-182. DOI: 10.5593/SGEM2014/B23/S10.022. ISBN 978-619-7105-12-4. ISSN 1314-2704.

\bibitem{H11} HOWELL, J.R. Thermal radiation heat transfer. 5th ed. Boca Raton: CRC Press, c2011, 957 s. ISBN 978-1-4398-0533-6.

\bibitem{J13} JONG, Edited by F.D. van der MEER and STEVEN M. de. Imaging spectrometry basic principles and prospective applications: basic principles and prospective applications. [Nachdr.]. Dordrecht: Springer, 2013. ISBN 978-0-306-47578-8.

\bibitem{K60} KIRCHHOFF, G. Ueber das Verhältniss zwischen dem Emissionsvermögen und dem Absorptionsvermögen der Körper für Wärme und Licht. \textit{Annalen der Physik und Chemie}. 1860, vol. 185, issue 2, s. 275-301 [cit. 2015-04-24]. DOI: 10.1002/andp.18601850205.

\bibitem{LZ13} LI, Z., B. TANG, H. WU, H. REN, G. YAN, Z. WAN, I.F. TRIGO and J.A. SOBRINO. Satellite-derived land surface temperature: Current status and perspectives. \textit{Remote Sensing of Environment} [online]. 2013, vol. 131, s. 14-37 [cit. 2015-04-24]. DOI: 10.1016/j.rse.2012.12.008.

\bibitem{M94} MATSUNAGA, T., 1994. A Temperature-Emissivity Separation Method Using an Empirical Relationship between the Mean, the Maximum, and the Minimum of the Thermal Infrared Emissivity Spectrum. \textit{Journal of the Remote Sensing Society of Japan}. vol. 14, i. 3, p. 230–241. Available at: doi:10.11440/rssj1981.14.230

\bibitem{M15} MODIS website [online]. [cit. 2015-05-06]. Dostupné z: http://modis.gsfc.nasa.gov/

\bibitem{NK14} NOTESCO, G., V. KOPAČKOVÁ, P. ROJÍK, G. SCHWARTZ, I. LIVNE and E. DOR. Mineral Classification of Land Surface Using Multispectral LWIR and Hyperspectral SWIR Remote-Sensing Data. A Case Study over the Sokolov Lignite Open-Pit Mines, the Czech Republic. Remote Sensing. 2014, vol. 6, issue 8, s. 7005-7025. DOI: 10.3390/rs6087005. Available at: http://www.mdpi.com/2072-4292/6/8/7005/

\bibitem{PP12} PIPIA, L., F. PEREZ, A. TARDA, L. MARTINEZ and R. ARBIOL. Simultaneous usage of optic and thermal hyperspectral sensors for crop water stress characterization. 2012 \textit{IEEE International Geoscience and Remote Sensing Symposium}. IEEE, 2012, s. 6661-6664. DOI: 10.1109/IGARSS.2012.6352071. Available at: http://ieeexplore.ieee.org/lpdocs/epic03/wrapper.htm?arnumber=6352071 

\bibitem{P00} PLANCK, M. Zur Theorie des Gesetzes der Energieverteilung im Normalspektrum. \textit{Verhandlungen der Deutschen Physikalischen Gesellschaft}. 1900, vol. 2, p. 237

\bibitem{PM05} POGORZALA, D., D. MESSINGER, C. SALVAGGIO and J. SCHOTT, 2005. Gas plume species identification in airborne LWIR imagery using constrained stepwise regression analyses. s. 194–205, Available at: doi:10.1117/12.603661

\bibitem{RC10} RIBEIRO DA LUZ, B. and J.K. CROWLEY. Identification of plant species by using high spatial and spectral resolution thermal infrared (8.0–$\SI{13.5}{\micro\meter}$) imagery. \textit{Remote Sensing of Environment}. 2010, vol. 114, issue 2, s. 404-413. DOI: 10.1016/j.rse.2009.09.019. Available at: http://linkinghub.elsevier.com/retrieve/pii/S0034425709002910

\bibitem{RS02} RICHTER, R. a D. SCHLÄPFER. Geo-atmospheric processing of airborne imaging spectrometry data. Part 2: Atmospheric/topographic correction. International Journal of Remote Sensing. 2002, 23(13), 2631-2649. DOI: 10.1080/01431160110115834. ISSN 0143-1161.

\bibitem{SG09} SABOL, Jr., D.E., A. R. GILLESPIE, E. ABBOTT and G. YAMADA. Field validation of the ASTER Temperature–Emissivity Separation algorithm. \textit{Remote Sensing of Environment}. 2009-11-16, vol. 113, issue 11, s. 2328-2344. DOI: 10.1016/j.rse.2009.06.008. Available at: http://linkinghub.elsevier.com/retrieve/pii/S0034425709001898

\bibitem{SF12} SOBRINO, J. A., B. FRANCH, C. MATTAR, J. C. JIMÉNEZ-MUÑOZ and C. CORBARI, 2012. A method to estimate soil moisture from Airborne Hyperspectral Scanner (AHS) and ASTER data: Application to SEN2FLEX and SEN3EXP campaigns. Remote Sensing of Environment. 15.2., roč. 117, s. 415–428. ISSN 0034-4257. Available at: doi:10.1016/j.rse.2011.10.018

\bibitem{SJ06} SOBRINO, J. A., J. C. JIMÉNEZ-MUÑOZ, P. J. ZARCO-TEJADA, G. SEPULCRE-CANTÓ and DE MIGUEL. Land surface temperature derived from airborne hyperspectral scanner thermal infrared data. Remote Sensing of Environment. 2006, vol. 102, 1-2. DOI: 10.1016/j.rse.2006.02.001.

\bibitem{SO12} SOBRINO, J. A., R. OLTRA-CARRIÓ, J. C. JIMÉNEZ-MUÑOZ, Y. JULIEN, G. SÒRIA, B. FRANCH and C. MATTAR, 2012. Emissivity mapping over urban areas using a classification-based approach: Application to the Dual-use European Security IR Experiment (DESIREX). \textit{International Journal of Applied Earth Observation and Geoinformation}. vol. 18, i. 0, s. 141–147. Available at: doi:http://dx.doi.org/10.1016/j.jag.2012.01.022

\bibitem{WQ11} WANG, H., Q. XIAO, H. LI and B. ZHONG. Temperature and emissivity separation algorithm for TASI airborne thermal hyperspectral data. In: \textit{2011 International Conference on Electronics, Communications and Control (ICECC)}. 2011 [cit. 2015-04-24]. DOI: 10.1109/icecc.2011.6066288.

\bibitem{WW11} WANG, N., H. WU, F. NERRY, C. LI and Z. LI. Temperature and Emissivity Retrievals From Hyperspectral Thermal Infrared Data Using Linear Spectral Emissivity Constraint. \textit{IEEE Transactions on Geoscience and Remote Sensing}. 2011, vol. 49, issue 4, s. 1291-1303. DOI: 10.1109/TGRS.2010.2062527. Available at: http://ieeexplore.ieee.org/lpdocs/epic03/wrapper.htm?arnumber=5567152

\bibitem{Y02} YOUNG, S.J. An in-scene method for atmospheric compensation of thermal hyperspectral data. \textit{Journal of Geophysical Research}. 2002, vol. 107, D24 [cit. 2015-04-24]. DOI: 10.1029/2001jd001266.

\bibitem{Z14} ZEMEK, František. \textit{Airborne remote sensing: theory and practice in assessment of terrestrial ecosystems.} Brno: Global Change Research Centre AS CR, c2014, 159 s. ISBN 978-80-87902-05-9.

\bibitem{van_der_meer_multi-_2012}
F.~D. van~der Meer, H.~M.~A. van~der Werff, F.~J.~A. van Ruitenbeek, C.~A.
  Hecker, W.~H. Bakker, M.~F. Noomen, M.~van~der Meijde, E.~J.~M. Carranza,
  J.~B.~d. Smeth, and T.~Woldai, ``Multi- and hyperspectral geologic remote
  sensing: {A} review,'' \emph{International Journal of Applied Earth
  Observation and Geoinformation}, vol.~14, no.~1, pp. 112--128, Feb. 2012.

\bibitem{pieri_aster_2004}
D.~Pieri and M.~Abrams, ``{ASTER} watches the world's volcanoes: a new paradigm
  for volcanological observations from orbit,'' \emph{Journal of Volcanology
  and Geothermal Research}, vol. 135, no. 1–2, pp. 13--28, Jul. 2004.

\bibitem{foster_physically_2012}
L.~Foster, B.~Brock, M.~Cutler, and F.~Diotri, ``A physically based method for
  estimating supraglacial debris thickness from thermal band remote-sensing
  data,'' \emph{Journal of Glaciology}, vol.~58, no. 210, pp. 677--691, Aug.
  2012.

\bibitem{scheidt_determining_2010}
S.~Scheidt, M.~Ramsey, and N.~Lancaster, ``Determining soil moisture and
  sediment availability at white sands dune field, new mexico, from apparent
  thermal inertia data,'' \emph{Journal of Geophysical Research: Earth
  Surface}, vol. 115, no.~F2, pp. n/a--n/a, 2010, f02019.

\bibitem{weng_modeling_2011}
Q.~Weng, U.~Rajasekar, and X.~Hu, ``Modeling {Urban} {Heat} {Islands} and
  {Their} {Relationship} {With} {Impervious} {Surface} and {Vegetation}
  {Abundance} by {Using} {ASTER} {Images},'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~49, no.~10, pp. 4080--4089, Oct. 2011.

\bibitem{french_detecting_2008}
A.~N. French, T.~J. Schmugge, J.~C. Ritchie, A.~Hsu, F.~Jacob, and K.~Ogawa,
  ``Detecting land cover change at the {Jornada} {Experimental} {Range}, {New}
  {Mexico} with {ASTER} emissivities,'' \emph{Remote Sensing of Environment},
  vol. 112, no.~4, pp. 1730--1748, Apr. 2008.

\bibitem{notesco_mineral_2014}
G.~Notesco, V.~Kopa\v{c}kov\'{a}, P.~Roj\'{i}k, G.~Schwartz, I.~Livne, and
  E.~B. Dor, ``Mineral {Classification} of {Land} {Surface} {Using}
  {Multispectral} {LWIR} and {Hyperspectral} {SWIR} {Remote}-{Sensing} {Data}.
  {A} {Case} {Study} over the {Sokolov} {Lignite} {Open}-{Pit} {Mines}, the
  {Czech} {Republic},'' \emph{Remote Sensing}, vol.~6, no.~8, pp. 7005--7025,
  Jul. 2014.

\bibitem{sobrino_method_2012}
J.~A. Sobrino, B.~Franch, C.~Mattar, J.~C. Jim\'{e}nez-Mu\~{n}oz, and
  C.~Corbari, ``A method to estimate soil moisture from {Airborne}
  {Hyperspectral} {Scanner} ({AHS}) and {ASTER} data: {Application} to
  {SEN}2flex and {SEN}3exp campaigns,'' \emph{Remote Sensing of Environment},
  vol. 117, pp. 415--428, Feb. 2012.

\bibitem{sobrino_emissivity_2012}
J.~A. Sobrino, R.~Oltra-Carri\'{o}, J.~C. Jim\'{e}nez-Mu\~{n}oz, Y.~Julien,
  G.~S\`{o}ria, B.~Franch, and C.~Mattar, ``Emissivity mapping over urban areas
  using a classification-based approach: {Application} to the {Dual}-use
  {European} {Security} {IR} {Experiment} ({DESIREX}),'' \emph{International
  Journal of Applied Earth Observation and Geoinformation}, vol.~18, pp.
  141--147, Aug. 2012.

\bibitem{pascucci_estimation_2014}
S.~Pascucci, R.~Casa, C.~Belviso, A.~Palombo, S.~Pignatti, and F.~Castaldi,
  ``Estimation of soil organic carbon from
  airborne hyperspectral thermal infrared data: {A} case study,''
  \emph{European Journal of Soil Science},
  vol.~65, no.~6, pp. 865--875, 2014.

\bibitem{pipia_simultaneous_2012}
L.~Pipia, F.~Perez, A.~Tarda, L.~Martinez, and R.~Arbiol, ``Simultaneous usage
  of optic and thermal hyperspectral sensors for crop water stress
  characterization,'' in \emph{Geoscience and {Remote} {Sensing} {Symposium}
  ({IGARSS}), 2012 {IEEE} {International}}, Jul. 2012, pp. 6661--6664.

\bibitem{li_satellite-derived_2013}
Z.-L. Li, B.-H. Tang, H.~Wu, H.~Ren, G.~Yan, Z.~Wan, I.~F. Trigo, and J.~A.
  Sobrino, ``Satellite-derived land surface temperature: {Current} status and
  perspectives,'' \emph{Remote Sensing of Environment}, vol. 131, pp. 14--37,
  Apr. 2013.

\bibitem{barducci_temperature_1996}
A.~Barducci and I.~Pippi, ``Temperature and emissivity retrieval from remotely
  sensed images using the ``{Grey} body emissivity'' method,'' \emph{IEEE
  Transactions on Geoscience and Remote Sensing}, vol.~34, no.~3, pp. 681--695,
  May 1996.

\bibitem{wang_temperature_2011-1}
N.~Wang, H.~Wu, F.~Nerry, C.~Li, and Z.-L. Li, ``Temperature and {Emissivity}
  {Retrievals} {From} {Hyperspectral} {Thermal} {Infrared} {Data} {Using}
  {Linear} {Spectral} {Emissivity} {Constraint},'' \emph{IEEE Transactions on
  Geoscience and Remote Sensing}, vol.~49, no.~4, pp. 1291--1303, Apr. 2011.

\bibitem{borel_error_2008}
C.~Borel, ``Error analysis for a temperature and emissivity retrieval algorithm
  for hyperspectral imaging data,'' \emph{International Journal of Remote
  Sensing}, vol.~29, no. 17-18, pp. 5029--5045, Sep. 2008.

\bibitem{gillespie_temperature_1998}
A.~Gillespie, S.~Rokugawa, T.~Matsunaga, J.~Cothern, S.~Hook, and A.~Kahle, ``A
  temperature and emissivity separation algorithm for {Advanced} {Spaceborne}
  {Thermal} {Emission} and {Reflection} {Radiometer} ({ASTER}) images,''
  \emph{IEEE Transactions on Geoscience and Remote Sensing}, vol.~36, no.~4,
  pp. 1113--1126, Jul. 1998.

\bibitem{sobrino_land_2006}
J.~A. Sobrino, J.~C. Jim\'{e}nez-Mu\~{n}oz, P.~J. Zarco-Tejada,
  G.~Sepulcre-Cant\'{o}, and E.~de~Miguel, ``Land surface temperature derived
  from airborne hyperspectral scanner thermal infrared data,'' \emph{Remote
  Sensing of Environment}, vol. 102, no. 1–2, pp. 99--115, May 2006.

\bibitem{jimenez-munoz_surface_2012}
J.~Jim\'{e}nez-Mu\~{n}oz, J.~Sobrino, and A.~Gillespie, ``Surface {Emissivity}
  {Retrieval} {From} {Airborne} {Hyperspectral} {Scanner} {Data}: {Insights} on
  {Atmospheric} {Correction} and {Noise} {Removal},'' \emph{IEEE Geoscience and
  Remote Sensing Letters}, vol.~9, no.~2, pp. 180--184, Mar. 2012.

\bibitem{wang_temperature_2011}
H.~Wang, Q.~Xiao, H.~Li, and B.~Zhong, ``Temperature and emissivity separation
  algorithm for {TASI} airborne thermal hyperspectral data,'' in \emph{2011
  {International} {Conference} on {Electronics}, {Communications} and {Control}
  ({ICECC})}, Sep. 2011, pp. 1075--1078.

\bibitem{sobrino_surface_2002}
J.~A. Sobrino, J.~C. Jim\'{e}nez-Mu\~{n}oz, J.~Labed-Nachbrand, and F.~Nerry,
  ``Surface emissivity retrieval from {Digital}
  {Airborne} {Imaging} {Spectrometer} data,''
  \emph{Journal of Geophysical
  Research-Atmospheres}, vol. 107, no. D23, p. 4729, Dec. 2002.

\bibitem{jimenez-munoz_temperature_2014}
J.~Jim\'{e}nez-Mu\~{n}oz, J.~Sobrino, C.~Mattar, G.~Hulley, and F.-M. Gottsche,
  ``Temperature and {Emissivity} {Separation} {From} {MSG}/{SEVIRI} {Data},''
  \emph{IEEE Transactions on Geoscience and Remote Sensing}, vol.~52, no.~9,
  pp. 5937--5951, Sep. 2014.

\bibitem{hulley_generating_2011}
G.~Hulley and S.~Hook, ``Generating {Consistent} {Land} {Surface} {Temperature}
  and {Emissivity} {Products} {Between} {ASTER} and {MODIS} {Data} for {Earth}
  {Science} {Research},'' \emph{IEEE Transactions on Geoscience and Remote
  Sensing}, vol.~49, no.~4, pp. 1304--1315, Apr. 2011.

\bibitem{mushkin_temperature/emissivity_2002}
A.~Mushkin, L.~K. Balick, and A.~R. Gillespie, ``Temperature/emissivity
  separation of {MTI} data using the {Terra}/{ASTER} {TES} algorithm,'' in
  \emph{Algorithms and Technologies for Multispectral, Hyperspectral, and
  Ultraspectral Imagery VIII}, vol. 4725, 2002, pp. 328--337.

\bibitem{hulley_hyspiri_2011}
G.~Hulley and S.~Hook, ``{HyspIRI} {Level}-2 {Thermal} {Infrared} ({TIR})
  {Land} {Surface} {Temperature} and {Emissivity} {Algorithm} {Theoretical}
  {Basis} {Document},'' Jet Propulsion Laboratory, California Institute of
  Technology, Pasadena, California, Tech. Rep., May 2011. [Online]. Available:
  \url{https://hyspiri.jpl.nasa.gov/downloads/Algorithm_Theoretical_Basis/HyspIRI_L2_Surface_Temperature_Emissivity_JPL_Pub_11-5_10102011.pdf}

\bibitem{fernandez-renau_inta_2005}
A.~Fern\'{a}ndez-Renau, J.~A. G\'{o}mez, and E.~de~Miguel, ``The {INTA} {AHS}
  system,'' in \emph{{SPIE} {Proceedings}}, vol. 5978, 2005, pp.
  59\,781L--59\,781L--8.

\bibitem{gillespie_lithologic_1986}
A.~R. Gillespie, ``Lithologic mapping of silicate rocks using {TIMS},'' Jet
  Propulsion Lab., California Inst. of Tech., Pasadena, CA, United States,
  Tech. Rep., Nov. 1986.

\bibitem{matsunaga_temperature-emissivity_1994}
T.~Matsunaga, ``A {Temperature}-{Emissivity} {Separation} {Method} {Using} an
  {Empirical} {Relationship} between the {Mean}, the {Maximum}, and the
  {Minimum} of the {Thermal} {Infrared} {Emissivity} {Spectrum},''
  \emph{Journal of the Remote Sensing Society of Japan}, vol.~14, no.~3, pp.
  230--241, 1994.

\bibitem{baldridge_aster_2009}
A.~M. Baldridge, S.~J. Hook, C.~I. Grove, and G.~Rivera, ``The {ASTER} spectral
  library version 2.0,'' \emph{Remote Sensing of Environment}, vol. 113, no.~4,
  pp. 711--715, Apr. 2009.

\bibitem{gustafson_revisions_2006}
W.~T. Gustafson, A.~R. Gillespie, and G.~J. Yamada, ``Revisions to the {ASTER}
  tem-perature/emissivity separation algorithm,'' \emph{Second Recent Advances
  in Quantitative Remote Sensing}, pp. 770--775, 2006.

\bibitem{sabol_field_2009}
J.~Sabol, Donald~E., A.~R. Gillespie, E.~Abbott, and G.~Yamada, ``Field
  validation of the {ASTER} {Temperature}–{Emissivity} {Separation}
  algorithm,'' \emph{Remote Sensing of Environment}, vol. 113, no.~11, pp.
  2328--2344, Nov. 2009.

\bibitem{bjorn_personal_communication}
B.~Eng, personal communication, 2015.

\bibitem{gillespie_temperature/emissivity_1999}
A.~R. Gillespie, S.~Rokugawa, S.~J. Hook, T.~Matsunaga, and A.~B. Kahle,
  ``Temperature/{Emissivity} {Separation} {Algorithm} {Theoretical} {Basis}
  {Document}, {Version} 2.4,'' Tech. Rep., Mar. 1999. [Online]. Available:
  \url{http://www.science.aster.ersdac.jspacesystems.or.jp/en/documnts/pdf/2b0304.pdf}

\bibitem{chedin_improved_1985}
A.~Chedin, N.~A. Scott, C.~Wahiche, and P.~Moulinier, ``The {Improved}
  {Initialization} {Inversion} {Method}: {A} {High} {Resolution} {Physical}
  {Method} for {Temperature} {Retrievals} from {Satellites} of the {TIROS}-{N}
  {Series},'' \emph{Journal of Climate and Applied Meteorology}, vol.~24,
  no.~2, pp. 128--143, Feb. 1985.

\bibitem{chevallier_neural_1998}
F.~Chevallier, F.~Ch\'{e}ruy, N.~A. Scott, and A.~Ch\'{e}din, ``A {Neural}
  {Network} {Approach} for a {Fast} and {Accurate} {Computation} of a
  {Longwave} {Radiative} {Budget},'' \emph{Journal of Applied Meteorology},
  vol.~37, no.~11, pp. 1385--1397, Nov. 1998.

\bibitem{gillespie_residual_2011}
A.~R. Gillespie, E.~A. Abbott, L.~Gilson, G.~Hulley, J.-C.
  Jim\'{e}nez-Mu\~{n}oz, and J.~A. Sobrino, ``Residual errors in {ASTER}
  temperature and emissivity standard products {AST}08 and {AST}05,''
  \emph{Remote Sensing of Environment}, vol. 115, no.~12, pp. 3681--3694, Dec.
  2011.

\bibitem{tonooka_verification_2001}
H.~Tonooka and F.~D. Palluconi, ``Verification of
  the {ASTER}/{TIR} atmospheric correction algorithm based on water surface
  emissivity retrieved,'' in \emph{Infrared
  {Spaceborne} {Remote} {Sensing} {Ix}}, M.~Strojnik and B.~F. Andresen,
  Eds.\hskip 1em plus 0.5em minus 0.4em\relax Bellingham: Spie-Int Soc Optical
  Engineering, 2001, vol. 4486, pp. 51--58.

\bibitem{tonooka_validation_2005}
H.~Tonooka and F.~Palluconi, ``Validation of {ASTER}/{TIR} standard atmospheric
  correction using water surfaces,'' \emph{IEEE Transactions on Geoscience and
  Remote Sensing}, vol.~43, no.~12, pp. 2769--2777, Dec. 2005.

\bibitem{tonooka_vicarious_2005}
H.~Tonooka, F.~Palluconi, S.~Hook, and T.~Matsunaga, ``Vicarious calibration of
  {ASTER} thermal infrared bands,'' \emph{IEEE Transactions on Geoscience and
  Remote Sensing}, vol.~43, no.~12, pp. 2733--2746, Dec. 2005.

\bibitem{coll_temperature_2007}
C.~Coll, V.~Caselles, E.~Valor, R.~Nicl\`{o}s, J.~M. S\'{a}nchez, J.~M. Galve,
  and M.~Mira, ``Temperature and emissivity separation from {ASTER} data for
  low spectral contrast surfaces,'' \emph{Remote Sensing of Environment}, vol.
  110, pp. 162--175, Sep. 2007.

\bibitem{sobrino_accuracy_2007}
J.~A. Sobrino, J.~C. Jim\'{e}nez-Mu\~{n}oz, L.~Balick, A.~R. Gillespie, D.~A.
  Sabol, and W.~T. Gustafson, ``Accuracy of
  {ASTER} level-2 thermal-infrared standard products of an agricultural area in
  {Spain},'' \emph{Remote Sensing of Environment}, vol. 106, no.~2, pp. 146--153, Jan. 2007.

\bibitem{tonooka_accurate_2005}
H.~Tonooka, ``Accurate atmospheric correction of {ASTER} thermal infrared
  imagery using the {WVS} method,'' \emph{IEEE Transactions on Geoscience and
  Remote Sensing}, vol.~43, no.~12, pp. 2778--2792, Dec. 2005.

\bibitem{software:SparCal} ITRES. SparCal [software]. [access  1.3.2016]. Available at: http://www.itres.com/supporting-products/

\bibitem{software:RCX} ITRES. RCX [software]. [access 1.3.2016]. Available at: http://www.itres.com/supporting-products/

\bibitem{software:GCSS} ITRES. GCSS [software]. [access 1.3.2016]. Available at: http://www.itres.com/supporting-products/

\end{thebibliography}